Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-06 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:06	14:13:20	(Sun 6.Sep)

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{LCA images using different window database sizes. The window boundaries are the same.}\label{oversampling_mosaic}
\end{figure*}

@@

\newpage
\section{Results and Discussion}

@@

A quick summary of the results and the order they will be presented is as follows:

@@

>>>>

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{LCA images using different window database sizes. The window boundaries are the same. The upper left image is identical to a rectangularly weighted DAS. Observe that sampling the $\beta$-range more finely increases the sidelobe suppression but leaves resolution unchanged. Adding more steering-variations improves both sidelobe suppression and resolution. However, using more than  $N_\beta=2$ window types and $N_\beta=3$ steering angles makes minimal difference.}\label{oversampling_mosaic}
\end{figure*}

@@

\section{Results and Discussion}

@@

\subsection{Summary}

The results and the order they will be presented is as follows:

@@

So far we have determined it reasonable to use Kaiser windows in the range $\beta\in[0,5]$, steered within the range $|\phi|\in[0,\phi_\mathrm{3dB}]$. But many windows do we need in these ranges?

In \Fig{oversampling_mosaic} we have compared LCA images made from windows databases of different sizes, but with the same parameter boundaries. We included the results from using a single window ($N_\beta=1$) and steering angle ($N_\phi=1$), which corresponds to a rectangularly weighted DAS.

Observe that sampling the $\beta$-range more finely increases the sidelobe suppression but leaves resolution unchanged. Adding more steering-variations improves both sidelobe suppression and resolution.

However, using more than  $N_\beta=2$ window types and $N_\beta=3$ steering angles makes minimal

\ref{oversampling_mosaic}
